Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
conclusion edit

\citet{kamil2016verified} propose \emph{verified lifting} to extract a
functionally-complete mathematical representation of low-level, and
potentially optimised, stencils in Fortran code. This extracted
predicate representation of a stencil is used to generate code
for the \textsc{Halide} high-performance
compiler~\citep{ragan2013halide}. Thus their approach must capture the
full meaning of a stencil computation which requires significant
program analysis. For example, they report that some degenerate
stencil kernels take up to 17 hours to analyse and others require
programmer intervention for correct invariants to be inferred.

>>>>

\citet{kamil2016verified} propose \emph{verified lifting} to extract a
functionally-complete mathematical representation of low-level, and
potentially optimised, stencils in Fortran code. This extracted
predicate representation of a stencil is used to generate code
for the \textsf{Halide} high-performance
compiler~\citep{ragan2013halide}. Thus their approach must capture the
full meaning of a stencil computation which requires significant
program analysis. For example, they report that some degenerate
stencil kernels take up to 17 hours to analyse and others require
programmer intervention for correct invariants to be inferred.
